The imprint of global magma oceans on exoplanet demographics

### 2023-02-07 src/tex/ms.tex
minor edits

% Define document class
%\documentclass[twocolumn]{aastex631}
\documentclass[modern]{aastex631}

@@

\subsection{Detecting the runaway greenhouse transition with current and planned exoplanet missions}
\todo{Introduce survey simulation(s). PLATO, (Ariel, LIFE(reach out to team; Hendrik Linz produced a LIFE Technology Overview document)) ?, Nautilus\\ What are threshold missions that are able to detect this signal? =>X meter working for Y years, or X' meter working for Y' years => conclusion could be that there is interesting science to do with intermediate size telescope.}
Under real-world conditions, the planetary properties in question can only be probed with a finite precision that is specific to each exoplanet mission.
%\subsubsection{PLATO}
\plato\ (PLAnetary Transits and Oscillation of stars) is an ESA mission designed to characterize terrestrial planets in the habitable zones of Sun-like stars, a goal to be achieved via long-term high-precision photometric monitoring of a sample of bright stars~\citep{Rauer2016}.
The \plato\ team has released an estimate on the number of exoplanets that will be characterized in the course of the main survey mission (Matuszewski, priv. comm.).
In the FGK sample of the mission, a minimum of 500 Earth-sized (\SIrange{0.8}{1.25}{\rEarth}) planets are expected to be detected.
\plato's definition study report~\citep{plato2017} further states precision requirements for planet radii~(\SI{3}{\percent}), planet masses through radial velocity follow-up~(\SI{10}{\percent}), and stellar masses, radii, and ages~(\SI{10}{\percent}).
We base our assessment of \plato's diagnostic power on these estimates.

    \begin{figure*}[ht!]
%    \script{figurescript.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/plato_fgrid.pdf}
            \caption{
            Expected delta-evidences as a function of the fraction of planets harboring runaway greenhouse climates for different versions of the \plato\ survey.
            Median and $[16\mathrm{th}, 84\mathrm{th}]$ percentiles of randomized survey simulations are shown; $\Delta \ln Z > 3$ (gray horizontal line) is considered sufficient evidence to reject the null hypothesis.
            \textit{Left:} For a large planet yield of $N = \var{Nplato}$, even small planet fractions $\sim \var{platoMinfrgh}$ allow a detection.
                A sample of 100 planets is sufficient if their masses are constrained to within \SI{10}{\percent} (dotted green line).
                Without such follow-up measurements, sufficient diagnostic power can only be achieved with this sample if $f_\mathrm{rgh} \gtrsim \var{platoMinfrghHundred}$.
               Even smaller samples are unlikely to yield a significant detection.
            \textit{Right:} Evidences when only FGK or only M~dwarfs are considered.
                Only M~dwarfs host enough planets on both sides of the threshold instellation to allow a reliable detection of the runaway greenhouse signal.
            }
            \label{fig:plato_fgrid}
        \end{centering}
    \end{figure*}

For a volume-limited sample of \var{Nplato} planets, considering all host star spectral types, we find that \plato\ is able to obtain a significant detection if the fraction of runaway greenhouse planets is larger than $\sim \var{platoMinfrgh}$ (see Fig.~\ref{fig:plato_fgrid}).
The minimum needed fraction rises to \var{platoMinfrghHundred} for $N = 100$.
For much smaller samples, even an optimistically strong signal can no longer be detected.

@@

\subsubsection{Constraining the threshold instellation}
\todo[inline]{for different survey modes, compare the constraints on  $S_{thresh}$.
Plot posteriors from random draws of simulations.}

@@

\todo[inline]{Maps to Sect. \ref{sec:statpower_missions}.}

\begin{note}
    \citet{Penny2019} mention that a significant increase in planet yield could be achieved if the telescope's slew speed was increased.
\end{note}

@@

\subsection{Mission design trades}\label{sec:mission-design-trades}
We now turn to mission design trades that influence the statistical power for testing the runaway greenhouse hypothesis.
...
\begin{note}
...FOLLOW-UP...

@@

\begin{note}
    ...FGK vs. M...:

>>>>

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{amssymb}
%\documentclass[modern]{aastex631}

@@

\subsection{Detecting the runaway greenhouse transition with current and planned exoplanet missions}
\todo{Introduce survey simulation(s). PLATO, Cheops, (Ariel, LIFE/LIFE precursor, Nautilus)\\ What are threshold missions that are able to detect this signal? =>X meter working for Y years, or X' meter working for Y' years => conclusion could be that there is interesting science to do with intermediate size telescope.}
Under real-world conditions, the planetary properties in question can only be probed with a finite precision that is specific to each exoplanet mission.
%\subsubsection{PLATO}
\plato\ (PLAnetary Transits and Oscillation of stars) is an ESA mission designed to characterize terrestrial planets in the habitable zones of Sun-like stars, a goal to be achieved via long-term high-precision photometric monitoring of a sample of bright stars~\citep{Rauer2016}.
The \plato\ team has released an estimate on the number of exoplanets that will be characterized in the course of the main survey mission (Matuszewski, priv. comm.).
In the FGK sample of the mission, several hundred Earth-sized (\SIrange{0.8}{1.25}{\rEarth}) planets are expected to be detected.
\plato's definition study report~\citep{plato2017} further states precision requirements for planet radii~(\SI{3}{\percent}), planet masses through radial velocity follow-up~(\SI{10}{\percent}), and stellar masses, radii, and ages~(\SI{10}{\percent}).
We base our assessment of \plato's diagnostic power on these estimates.

    \begin{figure*}[ht!]
%    \script{figurescript.py}
        \begin{centering}
            \includegraphics[width=\linewidth]{figures/plato_fgrid.pdf}
            \caption{
            Expected delta-evidences as a function of the fraction of planets harboring runaway greenhouse climates for different versions of the \plato\ survey.
            Median and $[16\mathrm{th}, 84\mathrm{th}]$ percentiles of randomized survey simulations are shown; $\Delta \ln Z > 3$ (gray horizontal line) is considered sufficient evidence to reject the null hypothesis.
            \textit{Left:} For a large planet yield of $N = \var{N_plato}$, even small planet fractions $\sim \var{platoMinfrgh}$ allow a detection.
                A sample of 100 planets is sufficient if their masses are constrained to within \SI{10}{\percent} (dotted green line).
                Without such follow-up measurements, sufficient diagnostic power can only be achieved with this sample if $f_\mathrm{rgh} \gtrsim \var{platoMinfrghHundred}$.
               Even smaller samples are unlikely to yield a significant detection.
            \textit{Right:} Evidences when only FGK or only M~dwarfs are considered.
                Only M~dwarfs host enough planets on both sides of the threshold instellation to allow a reliable detection of the runaway greenhouse signal.
            }
            \label{fig:plato_fgrid}
        \end{centering}
    \end{figure*}

For a volume-limited sample, considering all host star spectral types, we find that a yield of \var{N_plato} planets enables a significant detection if the fraction of runaway greenhouse planets is larger than $\sim \var{platoMinfrgh}$ (see Fig.~\ref{fig:plato_fgrid}).
The minimum needed fraction rises to \var{platoMinfrghHundred} for $N = 100$.
For much smaller samples, even an optimistically strong signal can no longer be detected.

@@

\subsubsection{Constraining the threshold instellation}
\todo[inline]{for different survey modes, compare the constraints on  $S_{thresh}$.
Plot posteriors from random draws of simulations.}
A key constraint resulting from a successful detection is a measurement of $S_{thresh}$.
Here, we assess the ability of different mission concepts explored above to constrain this parameter.
...

@@

%\todo[inline]{Maps to Sect. \ref{sec:statpower_missions}.:}
%\begin{note}
%    \citet{Penny2019} mention that a significant increase in planet yield could be achieved if the telescope's slew speed was increased.
%\end{note}

@@

\subsection{Mission design trades}\label{sec:mission-design-trades}
We now turn to mission design trades that influence the statistical power for testing the runaway greenhouse hypothesis.
...
\subsubsection{The value of follow-up campaigns}
\begin{note}
...FOLLOW-UP...radial velocity follow-up measurements...

@@

\subsubsection{Target star spectral types}
\begin{note}
    ...FGK vs. M...:
